Methodology for Assessing the State of the Practice for Domain X

### 2020-10-12 StateOfPractice/Methodology/Methodology.tex

\section{Domain Analysis} \label{SecDomainAnalysis}
\pmi{SS:"We should have more of an introduction on what is a commonality analysis, and more generally, what is a program family. We should also have more of a literature review, and a pointer to examples. Some publications to look at include ArdisAndWeiss1997, Chen2003, SmithAndChen2004, SmithEtAl2008, SmithMcCutchanAndCarette2017, Weiss1998"}
The domain analysis consists of a commonality analysis of the software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. The final result of the analysis will be tables of commonalities, variabilities and parameters of variation.

\noindent Steps to produce a commonality analysis:
\begin{enumerate}
\item Write an Introduction
\item Write the Overview of Domain
\item List Commonalities
\item List Variabilities
\item List Parameters of Variation
\item Add Terminology, Definitions, Acronyms
\end{enumerate}

>>>>

\section{Domain Analysis} \label{SecDomainAnalysis}

The domain analysis consists of a commonality analysis of the family of software packages. Its purpose is to show the relationships between these packages, and to facilitate an understanding of the informal specification and development of them. \cite{weiss1997defining} defines commonality analysis as an ``approach to defining a family by identifying commonalities, i.e., assumptions that are true for all family members, variabilities, i.e., assumptions about what can vary among family members, and common terminology for the family''.  The final result of the domain analysis will be tables of commonalities, variabilities, and parameters of variation of a program family, which \cite{parnas1976design} defines as ``a set of programs whose common properties are so extensive that it is advantageous to study the common properties of the programs before analyzing individual members''. \cite{smith2008commonality} present a template for conducting a commonality analysis, which was referred to when conducting this work. \cite{weiss1998commonality} describes another commonality analysis technique for deciding the members of a program family which readers are encouraged to be familiar with. \cite{SmithAndChen2004} provide an example of a commonality analysis for mesh generating software. The steps to produce a commonality analysis are:

\begin{enumerate}
\item Write an Introduction
\item Write the Overview of Domain
\item List Commonalities
\item List Variabilities
\item List Parameters of Variation
\item Add Terminology, Definitions, Acronyms
\end{enumerate}
